plottingScript

### 2023-04-27 analyses/plotter.Rmd
applied Rob's comments

g<-plot_grid(pt, legend,ncol = 1, rel_heights = c(1, .1), rel_widths = c(3, .4))
pdf(file="../StatPaper/figures/megaPlot.pdf",width=16,height=9)
g
dev.off()
```

@@

  rows<-apply(sumer,2,function(x){which(x==max(x))})
  cols<-c()
  for(i in 1:length(rows)){
    cols<-append(cols,rep(i,length(rows[[i]])))
  }
  rows<-c(5,as.vector(unlist(rows)))
  picks<-data.frame(row=rows,
                    col=c(0,cols))
  return(picks)
}

@@

  #ft$header$styles$text$bold$data
  ft <- add_header_row(x = ft,top=F, values = c("Method", 25,50,75,100,25,50,75,100),
                       colwidths = c(1,1,1,1,1,1,1,1,1))
  ft$header$styles$text$bold$data[1,1]<-T
  #ft <- add_header_row(
  #  x = ft, values = c(title),
  #  colwidths = c(9))
  ft <- align(ft, i = c(1,2), part = "header", align = "center")
  ft<-vline(ft, j = c(1,5), border = bord2, part = "body")
  ft<-hline(ft,i=c(1,2),border=bord2,part="header")
  #ft<-hline(ft,i=c(1),border=bord,part="body")
  ft<-fontsize(ft, i = NULL, j = NULL, size =7, part = "all")
  ft<-fontsize(ft, i = NULL, j = NULL, size =10, part = "header")
  ft <- align(ft, i = NULL, part = "body", align = "center")
  ft$body$styles$text$font.size$data[,1]<-10

@@

pdf(file="../StatPaper/figures/megaTable.pdf",width=14,height=13)
cowplot::plot_grid(cFlex,mFlex,fFlex,pFlex,ncol=1)
dev.off()

@@

pdf(file="../StatPaper/figures/winTable.pdf",width=12,height=6)
cowplot::plot_grid(cwtab,mwtab,fwtab,pwtab,ncol=2)
dev.off()

>>>>

g<-plot_grid(pt, legend,ncol = 1, rel_heights = c(1, .1), rel_widths = c(3, .4))
pdf(file="../StatPaper/figures/Figure2.pdf",width=16,height=9)
g
dev.off()
```

@@

  rows<-apply(sumer,2,function(x){which(x==max(x))})
  cols<-c()
  for(i in 1:length(rows)){
    cols<-append(cols,rep(i,length(rows[[i]])))
  }
  rows<-c(as.vector(unlist(rows)))
  picks<-data.frame(row=rows,
                    col=c(cols))
  return(picks)
}

@@

  #ft$header$styles$text$bold$data
  ft <- add_header_row(x = ft,top=F, values = c("Method","25%","50%","75%","100%",
                                                "25%","50%","75%","100%"),
                       colwidths = c(1,1,1,1,1,1,1,1,1))
  ft$header$styles$text$bold$data[1,1]<-T
  #ft <- add_header_row(
  #  x = ft, values = c(title),
  #  colwidths = c(9))
  ft <- align(ft, i = c(1,2), part = "header", align = "center")
  ft<-vline(ft, j = c(1,5), border = bord2, part = "body")
  ft<-hline(ft,i=c(1,2),border=bord2,part="header")
  #ft<-hline(ft,i=c(1),border=bord,part="body")
  ft<-fontsize(ft, i = NULL, j = NULL, size =7, part = "all")
  ft<-fontsize(ft, i = NULL, j = NULL, size =10, part = "header")
  ft <- align(ft, i = NULL, part = "body", align = "center")
  ft$body$styles$text$font.size$data[,1]<-10

@@

pdf(file="../StatPaper/figures/Table2.pdf",width=14,height=13)
cowplot::plot_grid(cFlex,mFlex,fFlex,pFlex,ncol=1)
dev.off()

@@

pdf(file="../StatPaper/figures/Table1.pdf",width=12,height=6)
cowplot::plot_grid(cwtab,mwtab,fwtab,pwtab,ncol=2)
dev.off()
